The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-17 analysis/paper/paper.qmd
minor changes

## Read only metadata for theses with PDF available
emu_theses <- 
  read_csv(here(data_path, "theses-metadata.csv")) %>%
  mutate(text = "") %>%
  filter(!is.na(pdf_via))

@@

# Preview theses in increasing order of graduation year
emu_theses %>% 
  arrange(graduation_year) %>% 
  pull(text_clean) %>% 
  head_text(head_n = 5)

@@

stop_words_custom <- emu_theses %>% 
  unnest_tokens(output = word, input = title) %>%   ### add words from the title
  select(word) %>% 
  rbind(., data.frame(word = c("preface", "foreword", "introduction", "conclusion", "thesis", 
                               "source", "author"))) %>% 
  # rbind(., data.frame(word = c("city", "urban", "urbanism"))) %>% 
  rbind(., data.frame(word = c("hab", "km")))

emu_theses_words <- emu_theses %>%
  mutate(author = paste(first_name, last_name)) %>% 
  select(author, title, text, -c(graduation_year, first_name, last_name)) %>% 
  unnest_tokens(output = word, input = text) %>%   # remove punctuation, convert to lowercase, seperate all words
  anti_join(stop_words, by = "word") %>%  # remove stop words
  anti_join(stop_words_custom, by = "word")
```

@@

emu_theses_words %>% 
  mutate(stem = wordStem(words = word, 
                         language = "porter")) %>%  # Implement the Porter stemming algorithm for English provided by the SnowballC package
  count(stem, sort = TRUE)
```

@@

emu_theses_bigrams_top <- emu_theses_bigrams %>%
  group_by(title) %>%
  count(bigram, sort = TRUE) %>%
  slice_max(n, n = 20) %>%        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  ungroup() %>% 
  mutate(bigram = reorder(bigram, n))

emu_theses_bigrams_top_all <- emu_theses_bigrams %>%
  count(bigram, sort = TRUE) %>%
  slice_max(n, n = 20) %>%        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  mutate(bigram = reorder(bigram, n))

emu_theses_bigrams_top %>%
  filter(title == unique(title)[1:6]) |> 
  ggplot(aes(x = bigram, y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2) +
  theme(legend.position = "none") 
```

>>>>

## Read only metadata for theses with PDF available
emu_theses <- 
  read_csv(here(data_path, "theses-metadata.csv")) |>
  mutate(text = "") |>
  filter(!is.na(pdf_via))

@@

# Preview theses in increasing order of graduation year
emu_theses |> 
  arrange(graduation_year) |> 
  pull(text_clean) |> 
  head_text(head_n = 5)

@@

stop_words_custom <- emu_theses |> 
  unnest_tokens(output = word, input = title) |>   ### add words from the title
  select(word) |>
  rbind(., data.frame(word = c("preface", "foreword", "introduction", "conclusion", "thesis", 
                               "source", "author"))) |>
  # rbind(., data.frame(word = c("city", "urban", "urbanism"))) %>% 
  rbind(., data.frame(word = c("hab", "km")))

emu_theses_words <- emu_theses |>
  mutate(author = paste(first_name, last_name)) |> 
  select(author, title, text, -c(graduation_year, first_name, last_name)) |> 
  unnest_tokens(output = word, input = text) |>   # remove punctuation, convert to lowercase, seperate all words
  anti_join(stop_words, by = "word") |>  # remove stop words
  anti_join(stop_words_custom, by = "word")
```

@@

emu_theses_words %>% 
  mutate(stem = wordStem(words = word, 
                         language = "porter")) |>  # Implement the Porter stemming algorithm for English provided by the SnowballC package
  count(stem, sort = TRUE)
```

@@

emu_theses_bigrams_top <- emu_theses_bigrams |>
  group_by(title) |>
  count(bigram, sort = TRUE) |>
  slice_max(n, n = 20) |>        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  ungroup() |>
  mutate(bigram = reorder(bigram, n))

emu_theses_bigrams_top_all <- emu_theses_bigrams |>
  count(bigram, sort = TRUE) |>
  slice_max(n, n = 20) |>        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  mutate(bigram = reorder(bigram, n))

emu_theses_bigrams_top |>
  filter(title == unique(title)[1:6]) |> 
  ggplot(aes(x = bigram, y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2) +
  theme(legend.position = "none") 
```
